\bf Excuse me, do you have a moment to talk about version control?

### 2017-05-30 README.tex
Re-render everything

Git has been re-purposed by the data science community
\citep{Ram2013, git-for-humans}. In addition to using it for source
code, we use it to manage the motley collection of files that make up
typical data analytical projects, which often consist of data, figures,
reports, and, yes, source code. Even those who identify more as
statistician than data scientist generally have a similar mix of files
that are the artifacts of a project.

@@

\textbf{Derived products:} These files are programmatically generated
from source files and have external value. By executing \texttt{.R} or
rendering \texttt{.Rmd} files, you obtain artefacts such as intermediate
data (e.g., \texttt{.csv} or \texttt{.rds}), figures (e.g.,
\texttt{.png} or \texttt{.pdf}), and reports (e.g., \texttt{.md},
\texttt{.pdf}, \texttt{.docx}, or \texttt{.html}).

@@

\subsection{GitHub as course management
system}\label{github-as-course-management-system}

\href{http://stat545.com}{STAT 545} is a data wrangling and analysis
course at the University of British Columbia. I was the instructor in
charge for several years, which coincided with my own adoption of
Git/GitHub. GitHub is used to manage the development of course material,
to serve the course website, to create a discussion forum, and to host
all student-submitted work.

Given that students must submit their work and provide peer review of
others' work via GitHub, the use of hosted version control is an
explicit, though modest, part of the course. The website
\href{http://happygitwithr.com}{Happy Git and GitHub for the useR} holds
our battle-tested instructions for setup and early usage. The students
achieve basic competence quite quickly and find it gratifying to see
their formatted, figure-rich R Markdown reports up on the internet.
Since it's easy to expose their work within the class, we conduct peer
review, which helps expertise to spread quickly through the group.

\subsubsection{Use a GitHub
Organization}\label{use-a-github-organization}

\href{https://help.github.com/articles/differences-between-user-and-organization-accounts/}{GitHub
Organizations} are ``shared accounts where groups of people can
collaborate across many projects at once''. This is the most appropriate
structure for stewarding course resources, since I can grant TAs and
students different levels of access to various repositories. Access can
be controlled at the individual user level or, more conveniently, for
entire \href{https://help.github.com/articles/setting-up-teams/}{Teams}.
The TA Team shares write access with me on a private repository for
internal matters. I provide each student with their own private
repository for coursework and grant other members of the Students Team
read access, in order to facilitate peer review. There is a public
repository that underpins the course website (see below). We have one
other public repository that exists solely so the
\href{https://github.com/STAT545-UBC/Discussion/issues}{Issues} can be
used as a discussion forum.

GitHub actively encourages the use of its platform in teaching. As an
instructor you can request a
\href{https://help.github.com/articles/discounted-organization-accounts/}{free
Organization account} that provides features normally available only on
paid plans, such as private repositories. In fact, GitHub provides
tooling for specific teaching workflows via
\href{https://classroom.github.com/}{GitHub Classroom}, although I do
not use it. That is not an intentional knock on their tools. I started
teaching with GitHub several years before this existed and developed a
different way of using the platform. I also find the
\href{https://education.github.com}{GitHub Education} resources to be
geared more towards computer science than data science.

\subsubsection{GitHub Pages for course
website}\label{github-pages-for-course-website}

All course content is provided on the \href{http://stat545.com}{STAT 545
website}. Each page is generated from an R Markdown document that is
rendered to HTML locally using the rmarkdown package, retaining the
intermediate Markdown. These pages are a mix of prose and rendered R
code, reflecting the live coding done in class. All of these files and
their history can be explored in the
\href{https://github.com/STAT545-UBC/STAT545-UBC.github.io}{source
repository}. The TA team has permission to write to this repo, meaning
they can (and do!) help me maintain the website. I rejoice that I am no
longer the webmaster. We also get typo corrections and other input from
the world at large, since this is entirely public.

If I were starting from scratch today, I would continue to use R
Markdown, RStudio, and GitHub Pages (see below), but would upgrade to a
more modern, automated approach to rendering the pages. I now recommend
\href{http://rmarkdown.rstudio.com/rmarkdown_websites.html}{R Markdown
websites}, \href{https://bookdown.org}{bookdown}, or
\href{https://bookdown.org/yihui/blogdown/}{blogdown} to manage the
process of creating a static website from a large and inter-related set
of \texttt{.Rmd} files.

GitHub offers several ways to host a website directly from a repository,
collectively known as
\href{https://help.github.com/categories/github-pages-basics/}{GitHub
Pages}. The STAT 545 website is a very simple
\href{https://help.github.com/articles/user-organization-and-project-pages/}{Organization
Page} that uses a
\href{https://help.github.com/articles/custom-domain-redirects-for-github-pages-sites/}{custom
domain}, \texttt{stat545.com}, instead of the default
\texttt{orgname.github.io}.

This system for managing course content is a great example of
integrating the doing of work and the sharing of it. We analyze data
live in class, using R, based on the scripts on the website. I re-render
the associated \texttt{.R} or \texttt{.Rmd}, commit the changed files,
push, and see it reflected right away on \url{http://stat545.com}. There
is no separation between having an idea, implementing it, and posting on
the website.

\subsubsection{Student-specific private
repos}\label{student-specific-private-repos}

Early in the course I elicit GitHub usernames for registered students,
via a \href{https://shiny.rstudio.com}{Shiny app}, and invite them to
join the course Organization. I then create one private repository per
student, in the STAT 545 Organization. The targeted student has write
access and the other students have read access. This is somewhat
controversial, due to the possibility of cheating, but I have seen more
pros than cons for this setup, in the STAT 545 context. In other
settings, I have also used one repo per student \emph{per homework
assignment}, which allows you to keep the repos completely private until
homework submission, then increase their visibility during marking and
peer review. Some courses will work better with one model or the other.

Each student does their work in this repo, submitting a major assignment
approximately once a week. The first assignment is simply to claim the
repository and create a README, which proves they have all the relevant
software setup and they can write a little Markdown. Each week we tackle
some new data analysis or wrangling task, with increasing latitude for
independence. Homework is implemented in R Markdown documents, rendered
to Markdown, and pushed to GitHub. Students submit their work by opening
an issue in their repo, naming the assignment in the title, providing
the SHA of the associated final commit, and linking to the main
\texttt{.md} file. We leave feedback as comments in the issue thread or,
occasionally, propose changes to code via ``pull requests''. Two peers
are selected at random to review each assignment, a process that we also
implement via GitHub Issues.

At the end of term, the student (and their instructor!) can visit the
repo to find an organized, navigable sequence of \textasciitilde{}10
assignments. Each student leaves with self-written documentation of
everything they've done, ready to consult in future projects. The last
assignments require writing an R package or Shiny app, which they
generally do in public repositories under their own accounts. They
finish STAT 545 with several months of Git/GitHub experience and the
start of a data science portfolio.

@@

Simply having a project on GitHub gives it a web presence! Non-users of
Git/GitHub can visit the project in the browser and interact with it
like a webpage. They can grab a snapshot of all the files as a ZIP
archive by simply clicking a button. People with GitHub accounts have
even more options. They can clone or fork the repository to get their
own copy, which also makes it easy for them to stay current on future
changes.

As described above, GitHub Pages offer various ways to serve proper
websites, even quite sophisticated ones, directly out of a GitHub repo.
But before you even worry about that, certain practices can make a
GitHub repository much more browsable. For many projects, this is more
than sufficient for granting people access to your work.

@@

*link to \url{http://happygitwithr.com/repo-browsability.html*}

@@

>>>>

Git has been re-purposed by the data science community
\citep{Ram2013, git-for-humans, ten-simple-rules-git}. We use it to
manage the motley collection of files that make up typical data
analytical projects, which often consist of data, figures, reports, and,
yes, source code. Even those who identify more as statistician than data
scientist generally have a similar mix of files that are the artifacts
of a project.

@@

\textbf{Derived products:} These files are programmatically generated
from source files and have external value. By executing \texttt{.R} or
rendering \texttt{.Rmd} files, you obtain artifacts such as intermediate
data (e.g., \texttt{.csv} or \texttt{.rds}), figures (e.g.,
\texttt{.png} or \texttt{.pdf}), and reports (e.g., \texttt{.md},
\texttt{.pdf}, \texttt{.docx}, or \texttt{.html}).

@@

@@

Simply having a project on GitHub gives it a web presence! Non-users of
Git/GitHub can visit the project in the browser and interact with it
like a webpage. They can grab a snapshot of all the files as a ZIP
archive by simply clicking a button. People with GitHub accounts can use
Git-specific methods to make their own copy, i.e.~a clone or a fork,
which make it easy to keep current with future changes.

GitHub offers several ways to host a proper website directly from a
repository, collectively known as
\href{https://help.github.com/categories/github-pages-basics/}{GitHub
Pages}. At one extreme, as long as you've got one Markdown file,
\href{https://github.com/blog/2289-publishing-with-github-pages-now-as-easy-as-1-2-3}{GitHub
Pages can create a simple website} automatically. At the other extreme,
sophisticated users can take full advantage of the
\href{https://jekyllrb.com}{Jekyll static site generator}. The STAT 545
website (\href{http://stat545.com}{stat545.com},
\href{https://github.com/STAT545-UBC/STAT545-UBC.github.io}{GitHub
repo}) falls on the more primitive side.
\href{http://rmarkdown.rstudio.com/rmarkdown_websites.html}{R Markdown
websites}, \href{https://bookdown.org}{bookdown}
\citep{bookdown-pkg, bookdown-book}, and
\href{https://bookdown.org/yihui/blogdown/}{blogdown} provide several
R-focused options for rendering the pages \emph{en masse}.

But even before you make an actual website, certain practices can
\href{http://happygitwithr.com/repo-browsability.html}{make your GitHub
repository much more browsable}. For many projects, this is more than
sufficient for helping people connect with your work.

@@

@@

A Quick Introduction to Version Control with Git and GitHub
\url{http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1004668}
